Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-06 3.phase_transitions/phase_transitions.tex
done
Implemented a more flexible support parameterization in Ch. 4.  All proposed changes are marked in blue. PLEASE REVIEW.

As laid out in Section \ref{sec:asymptotics}, we work under the asymptotic regime where the problem dimension 
$p$ diverges to infinity.  The set of non-zero entires of the signal vector $\mu = \mu_p$ will be referred
to as its {\em support} and denoted by 
$$
 S_p:=\{i\, :\, \mu(i)\not = 0\}.
$$
We shall assume that the size of the support is
\begin{equation} \label{eq:signal-sparsity-additive}
   \stilian{|S_p| \sim p^{1-\beta} }{\mbox{instead of $= \left\lfloor p^{1-\beta} \right\rfloor$ \fbox{CAN WE DO THAT?}}}, \quad \beta\in(0,1],
\end{equation}
where $\beta$ parametrizes the problem sparsity\stilian{, and $\sim$ stands for asymptotic equivalence, i.e., $a_p\sim b_p$ if $a_p/b_p\to 1$, as $p\to\infty$.}{}
The closer $\beta$ is to 1, the sparser the support $S_p$.  
Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with
\begin{equation} \label{eq:signal-size-additive}
    \underline{\Delta} = \sqrt{2\underline{r}\log{p}}
    \le \mu(i) \le
    \overline{\Delta} = \sqrt{2\overline{r}\log{p}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
for some constants $0<\underline{r}\le\overline{r}\le+\infty$.

>>>>

As laid out in Section \ref{sec:asymptotics}, we work under the asymptotic regime where the problem dimension 
$p$ diverges to infinity.  The set of non-zero entires of the signal vector $\mu = \mu_p$ will be referred
to as its {\em support} and denoted by 
$$
 S_p:=\{i\, :\, \mu(i)\not = 0\}.
$$
We shall assume that the size of the support is
\begin{equation} \label{eq:signal-sparsity-additive}
   |S_p| = \lfloor p^{1-\beta} \rfloor, \quad \beta\in(0,1],
\end{equation}
where $\beta$ parametrizes the problem sparsity.\stilian{A more general parameterization of the support involving a slowly 
varying function is considered in Chapter \ref{chap:exact-support-recovery}.}{}

The closer $\beta$ to 1, the sparser the support $S_p$. Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with
\begin{equation} \label{eq:signal-size-additive}
    \underline{\Delta} = \sqrt{2\underline{r}\log{p}}
    \le \mu(i) \le
    \overline{\Delta} = \sqrt{2\overline{r}\log{p}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
for some constants $0<\underline{r}\le\overline{r}\le+\infty$.

### 2021-04-06 4.exact_support_recovery/4.phase_transition_results.tex
done
Implemented a more flexible support parameterization in Ch. 4.  All proposed changes are marked in blue. PLEASE REVIEW.

Following \citet*{butucea2018variable}, we define the parameter space for the signals $\mu$ as
\begin{align} \label{eq:minimax-signal-config-over}
    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le \stilian{s_p^*}{\lfloor p^{1-\beta}\rfloor}, \nonumber \\
    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
\end{align}
\stilian{where $s_p^*$ is as in \eqref{eq:sparsity-parametrized-new}.}
Our first result states that, when $F\in \text{AGG}(\nu)$ with $\nu>0$, regardless of the error dependence structure, (asymptotic) perfect support recovery is achieved by applying Bonferroni's procedure with appropriately calibrated FWER, as long as the minimum signal size $\underline{r}$ is above the strong classification boundary \eqref{eq:strong-classification-boundary}.

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{if $\beta=1$, assume in addition that the
slowly varying function in \eqref{eq:sparsity-parametrized-new} is such that
\begin{equation}\label{e:new-beta=1-condition}
\ell(p) = o(F(- c\log(p)^{1/\nu})),\ \ \mbox{ for all $c>0$.}
\end{equation}}{}
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > f_{\mathrm{E}}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}
\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

@@

On the other hand, for the probability of no missed detection, we have:
\begin{equation*}
    \P\left[\widehat{S} \supseteq S\right] 
        = \P\left[\min_{i\in S}x(i) > t_p\right]
        = \P\left[\min_{i\in S}x(i) - (\nu\underline{r}\log p)^{1/\nu} > t_p - (\nu\underline{r}\log p)^{1/\nu} \right].
\end{equation*}
Since the signal sizes are no smaller than $(\nu\underline{r}\log p)^{1/\nu}$, we have
\begin{equation*}
    x(i) - \left(\nu\underline{r}\log{p}\right)^{1/\nu} \ge \epsilon(i), \quad \text{for all }i\in S,
\end{equation*}
and hence we obtain
\begin{equation} \label{eq:sufficient-proof-eq1}
    \P\left[\widehat{S} \supseteq S\right] \ge 
    \P\left[\min_{i\in S}\epsilon(i) > (\nu\log{(p/\alpha)})^{1/\nu}(1+o(1)) - (\nu\underline{r}\log p)^{1/\nu} \right],
\end{equation}
where we plugged in the expression for $t_p$ in \eqref{e:AGG-threshold}.
Now, since the minimum signal size is bounded below by $\underline{r} > \left(1 + (1-\beta)^{1/\nu}\right)^\nu$, we have $\underline{r}^{1/\nu}-(1-\beta)^{1/\nu}>1$, and so we can pick a $\delta > 0$ such that 
\begin{equation} \label{eq:choice-of-delta}
    \delta < \left(\underline{r}^{1/\nu} - (1-\beta)^{1/\nu}\right)^\nu - 1.
\end{equation}
Since by assumption, for all $\delta>0$, we have $p^{-\delta} = o\left(\alpha(p)\right)$, there is an
$M=M(\delta)$ such that $p/\alpha(p) < p^{1+\delta}$ for all $p\ge M$. Thus, from \eqref{eq:sufficient-proof-eq1}, we further conclude that for $p\ge M$ we have
\begin{align}
    \P\Big[\widehat{S} \supseteq S\Big]
      &\ge \P\Big[\min_{i\in S}\epsilon(i) > \left((1+\delta)\nu\log{p}\right)^{1/\nu}(1+o(1)) - (\nu\underline{r}\log p)^{1/\nu} \Big] \nonumber \\
      &= \P\Big[\max_{i\in S}\left(-\epsilon(i)\right) < \underbrace{\left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1))}_{=:\text{A}} \Big] \nonumber \\
      &\ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
      % &\ge 1 - |S|\times\P\Big[(-\epsilon(1)) \ge \left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1)) \Big] 
\end{align}
where $\overline{F}_-(x) = \P[-\epsilon(i)>x]$ is the survival function of the $(-\epsilon(i))$'s.
Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption that ${|S_p|}\le \stilian{s_p^*= \ell(p)p^{1-\beta}}{{\lfloor p^{1-\beta}\rfloor}}$. 
Therefore, the lower bound does not depend on $\mu$ (nor on the error dependence structure), and holds uniformly in the parameter space. In turn, we obtain 
\begin{equation} \label{eq:exact-supporot-recovery-FWNR}
    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}).
\end{equation}

@@

Let now $\beta\in (0,1)$ and $u_p^- :=  F_-^{\leftarrow}(1-1/p)$. 
The fact that $p\overline{F}_-(u_p^-) \le 1$, implies
\begin{equation}
    \stilian{s_p^*}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}) \le 
    \frac{\overline{F}_-\left(\text{B}\times{u_{s_p^*}^-}\right)} {\overline{F}_-\left({u_{s_p^*}}\right)} \label{eq:sufficient-proof-eq3}
    % \P\Big[\frac{\max_{i\in S}(-\epsilon(i))}{u_{|S|}}\frac{u_{|S|}}{u_{\lfloor p^{1-\beta}\rfloor}} < \underbrace{\frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right)}_{=:\text{B}}\Big], \label{eq:exact-supporot-recovery-FWNR}
\end{equation}
where $\text{B} := {\text{A}}/{u_{s_p^*}^-}$.

Notice that by assumption, the $-\epsilon(i)$'s are also 
AGG$(\nu)$ distributed and by Proposition \ref{prop:quantile}, 
$u_p^{-}:= F_-^{\leftarrow}(1-1/p) \sim (\nu \log(p))^{1/\nu}$,
as $p\to\infty$. Therefore, we have
\begin{equation} \label{eq:sufficient-proof-eq4}
    u_{s_p^*}^- \equiv u_{\ell(p)p^{1-\beta}}^-\sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu},
\end{equation}
\stilian{where we used the fact that $\log(\ell(p)) = o(\log(p))$. Hence,}{and} 
\begin{equation*}
\text{B} = \frac{\text{A}}{u_{s_p^*}^-}
= \frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right) \to c>1
\end{equation*}
as $p\to\infty$, by our choice of $\delta$ in \eqref{eq:choice-of-delta}.

@@

Formally, we define the parameter space for the signals $\mu$ to be
\begin{align} \label{eq:minimax-signal-config-under}
    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|=\lfloor p^{1-\beta}\rfloor, \nonumber \\
    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\}.
\end{align}

@@

Since the estimator $\widehat{S}_p = \{x(i) \ge t_p(x)\}$ is thresholding, exact support recovery takes place if and only if the threshold separates the signals and null part, i.e.,
\begin{equation*}
    \P[\widehat{S}_p = S_p] 
    = \P\left[\max_{i\in S^c}x(i) < t_p(x) \le \min_{i\in S}x(i)\right]
    \le \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right].
\end{equation*}
Since the right-hand-side does not depend on the procedure $\widehat{S}_p$, we also have
\begin{equation} \label{eq:classification-possible-dependent-proof-1}
    \sup_{\widehat{S}_p\in{\cal T}} \P[\widehat{S}_p = S_p] 
    \le \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right]
    \le \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
\end{equation}
where we used the assumption that the signal sizes are no greater than $\overline{\Delta}$.
Let $S^* = S_p^*$ be a sequence of support sets that maximize the right-hand-side of \eqref{eq:classification-possible-dependent-proof-1}, i.e., let
$$
S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| = \lfloor p^{1-\beta}\rfloor} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
$$
where ties can be broken lexicographically if multiple maximizers exist.
Then,
% Since there is only a finite number support set $S$ in $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we can bound \eqref{eq:classification-possible-dependent-proof-1} from above uniformly over $\mathcal{S}$ as well.
% In particular, let 
% $$
% S^* = S^*_p \in \argmax_{S\in{\mathcal{S}}}\P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
% $$
we obtain the following bound which only depends on $\overline{r}$ and the distribution of ${\cal E}$,
\begin{align}
    \sup_{\widehat{S}_p\in{\cal T}} \sup_{\mu\in\Theta^-_p(\beta,\overline{r})} \P[\widehat{S}_p = S_p] 
    % \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right]
    &\le \P\left[{\max_{i\in S^{*c}}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S^*}\epsilon(i)}\right] \nonumber \\
% \end{align}
% \begin{align}
% \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right]  
%   &= \P\left[\frac{\max_{i\in S^c}x(i)}{u_p} < \frac{\min_{i\in S}x(i)}{u_p}\right] \nonumber \\
%   &\le  \P\left[\frac{\max_{i\in S^c}\epsilon(i)}{u_p} < \frac{\min_{i\in S}\overline{\Delta} + \epsilon(i)}{u_p}\right] \nonumber \\
  &= \P\left[ \frac{M_{S^{*c}}}{u_p} < \frac{\overline{\Delta} - m_{S^*}}{u_p} \right], \label{eq:classification-possible-dependent-proof-2}
\end{align}
where $M_{S^{*c}} = \max_{i\in S^{*c}}\epsilon(i)$ and $m_{S^*} = \max_{i\in S^*}\left(-\epsilon(i)\right)$.
Since the error arrays ${\cal E}$ and $(-{\cal E})$ are URS by assumption, using the expression for the AGG quantiles \eqref{eq:AGG-quantiles}, we have
\begin{equation} \label{eq:classification-possible-dependent-proof-3}
    \frac{M_{S^{*c}}}{u_p} = \frac{M_{S^{*c}}}{u_{|S^{*c}|}} \frac{u_{|S^{*c}|}}{u_p} \xrightarrow{\P} 1,
\quad \text{and} \quad
\frac{m_{S^*}}{u_p} = \frac{m_{S^*}}{u_{|S^*|}} \frac{u_{|S^*|}}{u_p} \xrightarrow{\P} (1-\beta)^{1/\nu},
\end{equation}
so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds since ${u_{|S^*|}}/{u_p}$ vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.

@@

Our final comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
\begin{remark} \label{rmk:dependence-assumptions}
Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
\begin{equation}
    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
    = \begin{cases}
    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > f_{\mathrm{E}}(\beta),\\
    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < f_{\mathrm{E}}(\beta)\\
    \end{cases}
\end{equation}
where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.

>>>>

Following \citet*{butucea2018variable}, we define the parameter space for the signals $\mu$ as
\begin{align} \label{eq:minimax-signal-config-over}
    \Theta_p^+(\beta, \underline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }|S_p|\le \stilian{s_p^\dagger}{\lfloor p^{1-\beta}\rfloor}, \nonumber \\
    &\quad\quad\mu(i)\ge (\nu\underline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
\end{align}
\stilian{where $s_p^\dagger$ is as in \eqref{eq:sparsity-parametrized-new}.}
Our first result states that, when $F\in \text{AGG}(\nu)$ with $\nu>0$, regardless of the error dependence structure, (asymptotic) perfect support recovery is achieved by applying Bonferroni's procedure with appropriately calibrated FWER, as long as the minimum signal size $\underline{r}$ is above the strong classification boundary \eqref{eq:strong-classification-boundary}.

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{If $\beta=1$, assume in addition that the
slowly varying function in \eqref{eq:sparsity-parametrized-new} is such that
\begin{equation}\label{e:new-beta=1-condition}
\ell(p) = o\Big(1/ F(- c\log(p)^{1/\nu})\Big),\ \ \mbox{ for all $c>0$.}
\end{equation}}{}
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > f_{\mathrm{E}}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}
\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

@@

On the other hand, for the probability of no missed detection, we have:
\begin{equation*}
    \P\left[\widehat{S} \supseteq S\right] 
        = \P\left[\min_{i\in S}x(i) > t_p\right]
        = \P\left[\min_{i\in S}x(i) - (\nu\underline{r}\log p)^{1/\nu} > t_p - (\nu\underline{r}\log p)^{1/\nu} \right].
\end{equation*}
Since the signal sizes are no smaller than $(\nu\underline{r}\log p)^{1/\nu}$, we have
\begin{equation*}
    x(i) - \left(\nu\underline{r}\log{p}\right)^{1/\nu} \ge \epsilon(i), \quad \text{for all }i\in S,
\end{equation*}
and hence we obtain
\begin{equation} \label{eq:sufficient-proof-eq1}
    \P\left[\widehat{S} \supseteq S\right] \ge 
    \P\left[\min_{i\in S}\epsilon(i) > (\nu\log{(p/\alpha)})^{1/\nu}(1+o(1)) - (\nu\underline{r}\log p)^{1/\nu} \right],
\end{equation}
where we plugged in the expression for $t_p$ in \eqref{e:AGG-threshold}.
Now, since the minimum signal size is bounded below by $\underline{r} > \left(1 + (1-\beta)^{1/\nu}\right)^\nu$, we have $\underline{r}^{1/\nu}-(1-\beta)^{1/\nu}>1$, and so we can pick a $\delta > 0$ such that 
\begin{equation} \label{eq:choice-of-delta}
    \delta < \left(\underline{r}^{1/\nu} - (1-\beta)^{1/\nu}\right)^\nu - 1.
\end{equation}
Since by assumption, for all $\delta>0$, we have $p^{-\delta} = o\left(\alpha(p)\right)$, there is an
$M=M(\delta)$ such that $p/\alpha(p) < p^{1+\delta}$ for all $p\ge M$. Thus, from \eqref{eq:sufficient-proof-eq1}, we further conclude that for $p\ge M$ we have
\begin{align}
    \P\Big[\widehat{S} \supseteq S\Big]
      &\ge \P\Big[\min_{i\in S}\epsilon(i) > \left((1+\delta)\nu\log{p}\right)^{1/\nu}(1+o(1)) - (\nu\underline{r}\log p)^{1/\nu} \Big] \nonumber \\
      &= \P\Big[\max_{i\in S}\left(-\epsilon(i)\right) < \underbrace{\left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1))}_{=:\text{A}} \Big] \nonumber \\
      &\ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}), \label{eq:sufficient-proof-eq2}
      % &\ge 1 - |S|\times\P\Big[(-\epsilon(1)) \ge \left(\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}\right)(\nu\log{p})^{1/\nu}(1+o(1)) \Big] 
\end{align}
where $\overline{F}_-(x) = \P[-\epsilon(i)>x]$ is the survival function of the $(-\epsilon(i))$'s.
Notice that \eqref{eq:sufficient-proof-eq2} follows from the union bound and the assumption 
that  \stilian{${|S_p|}\le s_p^\dagger= \ell(p)p^{1-\beta}$ in \eqref{eq:minimax-signal-config-over}. }{${|S_p|}\le \lfloor p^{1-\beta}\rfloor$}. 
Therefore, the lower bound does not depend on $\mu$ (nor on the error dependence structure), and holds uniformly in the parameter space. In turn, we obtain 
\begin{equation} \label{eq:exact-supporot-recovery-FWNR}
    \inf_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \supseteq S_p] \ge 1 - \stilian{\ell(p)p^{1-\beta}}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}).
\end{equation}

@@

Let now $\beta\in (0,1)$ and $u_p^- :=  F_-^{\leftarrow}(1-1/p)$. 
The fact that $p\overline{F}_-(u_p^-) \le 1$, implies
\begin{equation}
    \stilian{s_p^\dagger}{\lfloor p^{1-\beta} \rfloor} \times \overline{F}_-(\text{A}) \le 
    \frac{\overline{F}_-\left(\text{B}\times{u_{s_p^\dagger}^-}\right)} {\overline{F}_-\left({u_{s_p^\dagger}}\right)} \label{eq:sufficient-proof-eq3}
    % \P\Big[\frac{\max_{i\in S}(-\epsilon(i))}{u_{|S|}}\frac{u_{|S|}}{u_{\lfloor p^{1-\beta}\rfloor}} < \underbrace{\frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right)}_{=:\text{B}}\Big], \label{eq:exact-supporot-recovery-FWNR}
\end{equation}
where $\text{B} := {\text{A}}/{u_{s_p^\dagger}^-}$.

Notice that by assumption, the $-\epsilon(i)$'s are also 
AGG$(\nu)$ distributed and by Proposition \ref{prop:quantile}, 
$u_p^{-}:= F_-^{\leftarrow}(1-1/p) \sim (\nu \log(p))^{1/\nu}$,
as $p\to\infty$. Therefore, we have
\begin{equation} \label{eq:sufficient-proof-eq4}
    u_{s_p^\dagger}^- \equiv u_{\ell(p)p^{1-\beta}}^-\sim \left(\nu(1-\beta)\log{p}\right)^{1/\nu},
\end{equation}
\stilian{where we used the fact that $\log(\ell(p)) = o(\log(p))$. Hence,}{and} 
\begin{equation*}
\text{B} = \frac{\text{A}}{u_{s_p^\dagger}^-}
= \frac{\underline{r}^{1/\nu} - (1+\delta)^{1/\nu}}{(1-\beta)^{1/\nu}}\left(1+o(1)\right) \to c>1
\end{equation*}
as $p\to\infty$, by our choice of $\delta$ in \eqref{eq:choice-of-delta}.

@@

Formally, we define the parameter space for the signals $\mu$ to be
\begin{align} \label{eq:minimax-signal-config-under}
    \Theta_p^-(\beta, \overline{r}) &= \{\mu\in\mathbb{R}^p:\;\text{there exists a set }S_p\subseteq\{1,\ldots,p\}\;\text{ such that }
    \stilian{|S_p| = \lfloor s_p^\dagger \rfloor}{ |S_p|=\lfloor p^{1-\beta}\rfloor}, \nonumber \\
    &\quad\quad0<\mu(i)\le(\nu\overline{r}\log{p})^{1/\nu}\;\text{for all }i\in S_p,\;\text{and }\mu(i)=0\;\text{for all }i\not\in S_p\},
\end{align}
\stilian{where $s_p^\dagger= \ell(p) p^{1-\beta}$ is as in \eqref{eq:sparsity-parametrized-new}.}

@@

Since the estimator $\widehat{S}_p = \{x(i) \ge t_p(x)\}$ is thresholding, exact support recovery takes place if and only if the threshold separates the signals and null part, i.e.,
\begin{equation*}
    \P[\widehat{S}_p = S_p] 
    = \P\left[\max_{i\in S^c}x(i) < t_p(x) \le \min_{i\in S}x(i)\right]
    \le \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right].
\end{equation*}
Since the right-hand-side does not depend on the procedure $\widehat{S}_p$, we also have
\begin{equation} \label{eq:classification-possible-dependent-proof-1}
    \sup_{\widehat{S}_p\in{\cal T}} \P[\widehat{S}_p = S_p] 
    \le \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right]
    \le \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
\end{equation}
where we used the assumption that the signal sizes are no greater than $\overline{\Delta}$.
Let $S^* = S_p^*$ be a sequence of support sets that maximize the right-hand-side of \eqref{eq:classification-possible-dependent-proof-1}, i.e., let
$$
S_p^* = \argmax_{S\subseteq\{1,\ldots,p\}:|S| =\stilian{\lfloor s_p^\dagger \rfloor }{\lfloor p^{1-\beta}\rfloor}} \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
$$
\stilian{where $s_p^\dagger = \ell(p)p^{1-\beta}$ is the size of the true support set and}{}
where ties can be broken lexicographically if multiple maximizers exist.
Then,
% Since there is only a finite number support set $S$ in $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we can bound \eqref{eq:classification-possible-dependent-proof-1} from above uniformly over $\mathcal{S}$ as well.
% In particular, let 
% $$
% S^* = S^*_p \in \argmax_{S\in{\mathcal{S}}}\P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right],
% $$
we obtain the following bound which only depends on $\overline{r}$ and the distribution of ${\cal E}$,
\begin{align}
    \sup_{\widehat{S}_p\in{\cal T}} \sup_{\mu\in\Theta^-_p(\beta,\overline{r})} \P[\widehat{S}_p = S_p] 
    % \P\left[{\max_{i\in S^c}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S}\epsilon(i)}\right]
    &\le \P\left[{\max_{i\in S^{*c}}\epsilon(i)} < {\overline{\Delta} + \min_{i\in S^*}\epsilon(i)}\right] \nonumber \\
% \end{align}
% \begin{align}
% \P\left[\max_{i\in S^c}x(i) < \min_{i\in S}x(i)\right]  
%   &= \P\left[\frac{\max_{i\in S^c}x(i)}{u_p} < \frac{\min_{i\in S}x(i)}{u_p}\right] \nonumber \\
%   &\le  \P\left[\frac{\max_{i\in S^c}\epsilon(i)}{u_p} < \frac{\min_{i\in S}\overline{\Delta} + \epsilon(i)}{u_p}\right] \nonumber \\
  &= \P\left[ \frac{M_{S^{*c}}}{u_p} < \frac{\overline{\Delta} - m_{S^*}}{u_p} \right], \label{eq:classification-possible-dependent-proof-2}
\end{align}
where $M_{S^{*c}} = \max_{i\in S^{*c}}\epsilon(i)$ and $m_{S^*} = \max_{i\in S^*}\left(-\epsilon(i)\right)$.
Since the error arrays ${\cal E}$ and $(-{\cal E})$ are URS by assumption, using the expression for the AGG quantiles \eqref{eq:AGG-quantiles}, we have
\begin{equation} \label{eq:classification-possible-dependent-proof-3}
    \frac{M_{S^{*c}}}{u_p} = \frac{M_{S^{*c}}}{u_{|S^{*c}|}} \frac{u_{|S^{*c}|}}{u_p} \xrightarrow{\P} 1,
\quad \text{and} \quad
\frac{m_{S^*}}{u_p} = \frac{m_{S^*}}{u_{|S^*|}} \frac{u_{|S^*|}}{u_p} \xrightarrow{\P} (1-\beta)^{1/\nu},
\end{equation}
so that the two random terms in probability \eqref{eq:classification-possible-dependent-proof-2} converge to constants.
Notice that the second relation in \eqref{eq:classification-possible-dependent-proof-3} holds by URS for any $\beta\in(0,1)$; when $\beta=1$, the relation holds because \stilian{$\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight while $0\le u_{|S^*|}/u_p \le u_{\ell(p)}/u_p \to 0$ since $\ell(p) = o(p)$. }{${u_{|S^*|}}/{u_p}$  vanishes while $\{{m_{S^*}}/{u_{|S^*|}}\}$ is tight.}

@@

Our final comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
\begin{remark} \label{rmk:dependence-assumptions}
Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where 
$\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};\stilian{|S| = \lfloor \ell (p) p^{1-\beta}\rfloor}{|S|=\lfloor p^{1-\beta}\rfloor}\right\}$, we have
\begin{equation}
    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
    = \begin{cases}
    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > f_{\mathrm{E}}(\beta),\\
    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < f_{\mathrm{E}}(\beta)\\
    \end{cases}
\end{equation}
where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.
